Master's Project Journal

### 2018-11-05 tex_files/Journal.tex
journal entry

>>>>

\section*{Phase Detection}
The next step then was to work on a phase detection mechanism for the ADPLL. First off I went down the simplest route and implemented a 1 bit bang-bang detector using just a single D flip flop. After meeting with Brian on Wednesday we discussed some of the challenges of implementing the phase detector on an FPGA. Foremost among these was the issue of metastability and the likelihood of both signals occurring at the same time. For an implementation on an ASIC where an arbitration circuit can be constructed using gates I do not have this luxury, as I am restricted to simple look-up table elements. As a temporary workaround for this we decided I would implement a phase detector with the assumption that the signals are synchronised to the FPGA clock.\\
Working under this assumption I created a phase detector which counts the number of FPGA clock cycles between edges of the two signals in question. In order to avoid issues where the rising edge of the second signal detected occurs very shortly before the next rising edge of the first signal detected the maximum phase difference that can be detected is the high time of the first signal.\\
This phase detector outputs signed 2s complement integers that can be fed directly into the loop filter which succeeds this block.

The problem that this introduces then is the minimum phase difference detectable is 2.5 nano seconds which equates to a 65 KHz frequency or a 4.5$^\circ$ phase deviation.
